### 2017-04-07 paper/intro.tex
pass on abstract and part of intro

At large organizations, the alternative of renting cloud
services\footnote{List of popular hosting cloud services:
  \url{https://clutch.co/cloud}} or even building proprietary
infrastructures to running tests is a legitimate approach to mitigate
the regression testing problem.  However, for projects with low
budgets and yet relatively heavy testing workloads, this solution may
not be economically viable.  For these cases, the use of commodity
hardware (\eg{}, existing workstations), emerges as an attractive
solution for running tests.  Furthermore, the proliferation of
multi-core CPUs and the increasing popularization of testing
frameworks and build systems, which today provide mature support for
parallelization, enable test execution speedups through increased CPU
usage~(see Section~\ref{sec:modes}).  These two elements~---~demand
for cost-effective test execution and supply of relatively inexpensive
testing infrastructures~---~led us to investigate the usage of
parallelism for running tests in public open-source projects.

@@

This paper reports on an empirical study we conducted to analyze the
impact of low-level parallelization to speedup testing in open-source
projects.  This is a relevant problem given the tremendous popularity
of open-source development and regression testing
research~\cite{yoo-harman-stvr2012}.  The dimensions of analysis we
considered in this study are as follows: potential, effectiveness,
adoption, and tradeoffs.  Each dimension focuses on one aspect of our
study.  The dimension \textbf{potential} measures the potential of
parallelization to reduce testing costs.  In the limit,
parallelization would be fruitless if all projects used short-running
test suites or if the bulk of execution cost was dominated by a
relatively small number of tests in the suite.  The dimension
\textbf{effectiveness} measures the observed impact of
parallelization\Comment{~---~when used in selected open-source
  projects~---~} on testing costs.  Intuitively, benefits are
proportional to the cost reduction that parallelization brings.  In
the limit, the overhead of spawning virtual machines or threads can
even result in added cost.  The dimension \textbf{adoption} evaluates
(i) how often open-source projects use parallelization schemes and
(ii) how developers involved in costly projects (not using test suite
parallelization) perceive this technology.  It is important to measure
resistance to the technology and its reasons.  Finally, the dimension
\textbf{tradeoff} evaluates the issues and benefits associated
with\Comment{running test suites with} different parallel
configurations.  Note that the configuration choice can affect both
test cost and test flakiness, which is caused by the non-determinism
resulted from running tests in different schedulings. Discovering
Pareto-efficient~\cite{hwang-masud-1979} configurations is important
to guide practitioners and future developments in this area.

>>>>

At large organizations, the alternative of renting cloud
services\footnote{List of popular hosting cloud services:
  \url{https://clutch.co/cloud}} or even building proprietary
infrastructures to running tests is a legitimate approach to mitigate
the regression testing problem.  However, for projects with low
budgets and yet relatively heavy testing workloads, this solution may
not be economically viable.  For these cases, the use of commodity
hardware (\eg{}, existing workstations), emerges as an attractive
solution for running tests.  Furthermore, the proliferation of
multi-core CPUs and the increasing popularization of testing
frameworks and build systems, which today provide mature support for
parallelization, enable test execution speedups through increased CPU
usage~(see Section~\ref{sec:modes}).  These two elements~---~demand
for cost-effective test execution and supply of relatively inexpensive
testing infrastructures~---~led us to investigate the usage of
parallelism to speed up test execution.  This paper reports on an
empirical study we conducted to analyze the usage and impact of
low-level parallelization in speeding up testing for open-source
projects.  This is a relevant problem given the tremendous popularity
of open-source development and regression testing
research~\cite{yoo-harman-stvr2012}.

@@

The dimensions of analysis we considered in this study are as follows:
potential, effectiveness, adoption, and tradeoffs.  Each dimension
focuses on one aspect of our study.  The dimension \textbf{potential}
measures the potential of parallelization to reduce testing costs.  In
the limit, parallelization would be fruitless if all projects used
short-running test suites or if the bulk of execution cost was
dominated by a single test in the suite.  The dimension
\textbf{effectiveness} measures the observed impact of
parallelization\Comment{~---~when used in selected open-source
  projects~---~} on testing costs.  Intuitively, benefits are
proportional to the cost reduction that parallelization brings.  In
the limit, the overhead of spawning virtual machines or threads can
even result in added cost.  The dimension \textbf{adoption} evaluates
(i) how often open-source projects use parallelization schemes and
(ii) how developers involved in costly projects (not using test suite
parallelization) perceive this technology.  It is important to measure
resistance to the technology and its reasons.  Finally, the dimension
\textbf{tradeoffs} evaluates the issues and benefits associated
with\Comment{running test suites with} different parallel
configurations.  Note that the configuration choice can affect both
test cost and test flakiness, which is caused by the non-determinism
resulted from running test methods and classes in different
orderings.

%% Discovering Pareto-efficient~\cite{hwang-masud-1979}
%% configurations is important to guide practitioners and future
%% developments in this area.
